Energy and the CES production function

### 2015-10-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Updates for AllOE.

      # store the result in our list
      modelsCSP[[country]][[adj]][["noE"]][["CD"]] <- cdModCSP
      # CES
      # The only CES models that can adhere to the CSP are models where
      # alpha values are constant with respect to time. 
      # I.e., models where energy is not included AND where rho_1 = 0.
      # CES models where rho_1 = 0 are the Cobb-Douglas model.
      # Convienently, we previously fit that model.
      cesModCSP <- cdModCSP

@@

AllOE <- 
  leaf_apply(
    models, 
    class = "cesModel", 
    mod2oedf
  ) %>% 
  bind_rows() %>%
  # None of "models" adheres to the CSP.
  mutate (CSP = "w/o CSP")

# Now append to AllOE time-varying output elasticities from models that adhere to the CSP.
# These output elasticities are stored with variable names oe1, oe2, and oe3 in the data object in the models.
# See the <<Models_CSP>> chunk above.
# Uncomment when we're ready to add the CSP models to the alpha vs. time graph.

# AllOE <- leaf_apply(modelsCSP, class="lm", f=function(mod, id){
#   id_components <- strsplit(id, split = "[.]")[[1]]
#   if (id_components[4] == "CES") {
#     return(mod$data)
#   } else {
#     return(NULL)
#   }
# }) %>% 
#   do.call(plyr::rbind.fill, .) %>%
#   bind_rows(AllOE, .)

>>>>

      # store the result in our list
      modelsCSP[[country]][[adj]][["noE"]][["CD"]] <- cdModCSP
      # CES
      # The only CES models that can adhere to the CSP are models where
      # alpha values are constant with respect to time. 
      # I.e., models where energy is not included AND where rho_1 = 0.
      # CES models where rho_1 = 0 are the Cobb-Douglas model.
      # Convienently, we previously fit that model 
      # with the required output elasticities.
      cesModCSP <- cdModCSP

@@

AllOE <- 
  leaf_apply(models, class = "cesModel", mod2oedf) %>% 
  bind_rows() %>%
  # None of "models" adheres to the CSP.
  mutate (CSP = "w/o CSP")

# Now append to AllOE time-varying output elasticities from models that adhere to the CSP.

AllOE <- leaf_apply(modelsCSP, class="cesModel", f=mod2oedf) %>% 
  bind_rows() %>%
  mutate (CSP = "w/ CSP") %>%
  bind_rows(AllOE, .)
